---
title: "RR_1"
author: "SS"
date: "Thursday, August 06, 2015"
output: html_document
---

Loading the data
```{r}
setwd("~/GitHub/RepData_PeerAssessment1/activity")
data1 <- read.csv("activity.csv")
```

Processing data to get rid of missing values
```{r}
data2 <- na.omit(data1)
head(data2)
```
Mean total number of Steps taken per day 
The following code uses the dplyr package to group data and then calculates the total number of steps taken per day. 
```{r}
library(dplyr)
daily <-  group_by(data2, date)
t <- summarise(daily, total1 = sum(steps))
```

Histogram of of total number of steps taken each day.

```{r}
hist(t$total1)
```
Calculating and reporting the mean and median of the total number of steps taken per day.
```{r}
mean1 <- mean(t$total1)
mean1
median1 <- median(t$total1)
median1
```
The mean of total number of steps taken per day is mean1

The median of total number of steps taken per day is median1


Aveage Daily Activity Pattern
Making  a time-series plot of the 5-minute interval and the average number of steps taken, averaged across all days.
```{r}
interval <-  group_by(data2, interval)
i <- summarise(interval, avg = mean(steps))
head(i)
plot(i$interval, i$avg, type = "l", xlab = "Interval", ylab = "Average Number of Steps", col = "blue", lwd = 2)
```
Calculating and reporting the interval containing the maximum number of steps.
```{r}
max_steps = i[(which.max(i$avg)),]$interval
max_steps
```
The interval containg the maximum number of steps is max_steps.


Imputing missing values

Calculating and reporting the total number of missing values in the dataset.

```{r}
sum(is.na(data1$steps))
```
The total number of missing values is ...

Filling in the missing values



